Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
add bibliography and first reference

%% FIXME: TODO: Insert Figure 1 here

@@

Scientific journals increasingly require the data and provenance for articles to
be available in a machine readable format. The DOI registrar that DAP uses,
DataCite [11], was setup to provide unique identifiers for data items that can
be attached to publications, which in turn may have their own DOIs.

@@

>>>>

@@

Scientific journals increasingly require the data and provenance for articles to
be available in a machine readable format. The DOI registrar that DAP uses,
DataCite \cite{Brase2009}, was setup to provide unique identifiers for data items that can
be attached to publications, which in turn may have their own DOIs.

@@

\bibliographystyle{splncs}
\bibliography{podd-bibliography}
